Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-17 paper/lostanlenRelevanceScattering.tex
shorten supplementary material

Time reversal of a real signal $\boldsymbol{x}(t)$ is equivalent
to the complex conjugation of its Fourier transform $\boldsymbol{\widehat{x}}(\omega$).
As a consequence, the Fourier transform modulus $\vert\boldsymbol{\widehat{x}}(\omega)\vert$
is not only invariant to translation, but also invariant to time reversal.
Yet, although invariance to translation is needed for classification,
invariance to time reversal is an undesirable property.

The situation is different in the time-frequency domain. If the wavelet
$\boldsymbol{\psi}(t)$ has a symmetric envelope, that is, if there
exists a phase shift $\varphi\in[0;2\pi[$ such that $\boldsymbol{\psi}(-t)=\mathrm{e}^{\mathrm{i}\varphi}\boldsymbol{\psi}(t)$,
the wavelet transform is covariant with respect to time reversal:
\begin{eqnarray*}
\mathbf{U}_{1}(\mathcal{W}_{\boldsymbol{\tau}}\boldsymbol{x})(t,\gamma) & = & \left|\mathrm{e}^{\mathrm{i}\varphi}\int_{-\infty}^{+\infty}\boldsymbol{x}(-t^{\prime})\boldsymbol{\psi}_{2^{\gamma},T(2^{\gamma})}(t^{\prime}-t)\;\mathrm{d}t^{\prime}\right|\\
 & = & \left|\mathrm{e}^{\mathrm{i}\varphi}\right|\times\left|\int_{-\infty}^{+\infty}\boldsymbol{x}(t^{\prime})\boldsymbol{\psi}_{2^{\gamma},T(2^{\gamma})}(-t-t^{\prime})\;\mathrm{d}t^{\prime}\right|\\
 & = & \mathbf{U}_{1}\boldsymbol{x}(t,\gamma).
\end{eqnarray*}
Gabor wavelets have a symmetric envelope, as they satisfy $\boldsymbol{\psi}(-t)=-\boldsymbol{\psi}(t)$,
i.e. $\varphi=\pi$. This is due to the fact that Gaussians have bell-shaped
symmetric envelopes. Therefore, the Gabor wavelet transform commutes
with time reversal: 
\[
\mathbf{U}_{1}(\mathcal{W}_{\boldsymbol{\tau}}\boldsymbol{x})(t,\gamma)=\mathbf{U}_{1}\boldsymbol{x}(-t,\gamma).
\]
A simple way to break this undesirable invariance is to choose $\boldsymbol{\psi}(t)$
as an asymmetric wavelet instead of a Gabor symmetric wavelet.

>>>>

Time reversal of a real signal $\boldsymbol{x}(t)$ is equivalent
to the complex conjugation of its Fourier transform $\boldsymbol{\widehat{x}}(\omega$).
As a consequence, the Fourier transform modulus $\vert\boldsymbol{\widehat{x}}(\omega)\vert$
is not only invariant to translation, but also invariant to time reversal.
Yet, although invariance to translation is needed for classification,
invariance to time reversal is an undesirable property.
A simple way to break invariance to time reversal is to choose $\boldsymbol{\psi}(t)$
as an asymmetric wavelet instead of a Gabor symmetric wavelet.
